A Comparison of Actor Critic and Policy Gradient \\ Algorithms for Learning Mechanical Designs

### 2022-04-22 Paper/PaperForReview.tex
blbubsfdblsdfbhusfdgb

The training hyperparameters were selected based on the algorithm author recommendations and StableBaselines3 experimental findings. The vales are displayed in Table~\ref{tab:training_hyperameters}. All of the hyperparameters, with the exception of the rollout (Learning Starts) and the replay buffer, were set according to StableBaselines3 standards. The rollout setting was defined such that the agent could search the design space at random, filling the replay buffer with enough experience to prevent the agent from converging to a design space that was not optimal. The replay buffer was sized proportional to the number of training steps due to system memory constraints.  
%
\begin{table}[t]
        \caption{TD3 Training Hyperparameters}
        \vspace{-4mm}
        \label{tab:training_hyperameters}
        \begin{center}
        \begin{tabular}{|c||c|}
        \hline
        Hyperameter                     & Value                           \\
        \hline
        Learning Rate, $\alpha$         & 0.001                           \\
        Learning Starts                 & 100 Steps                       \\
        Batch Size                      & 100 Transitions                 \\
        Tau, $\tau$                     & 0.005                           \\
        Gamma, $\gamma$                 & 0.99                            \\
        Training Frequency              & 1:Episode                       \\
        Gradient Steps                  & $\propto$ Training Frequency    \\
        Action Noise,  $\epsilon$       & None                            \\
        Policy Delay                    & 1 : 2 Q-Function Updates        \\
        Target Policy Noise, $\epsilon$ & 0.2                             \\
        Target Policy Clip, $c$         & 0.5                             \\
        Seed                            & 100 Random Seeds                \\
        \hline
        \end{tabular}
        \end{center}
        \vspace{-5mm}
\end{table}
%

>>>>

The training hyperparameters were selected based on the algorithm author recommendations and StableBaselines3 experimental findings. The vales are displayed in Table~\ref{tab:training_hyperameters}. All of the hyperparameters, with the exception of the rollout (Learning Starts) and the replay buffer, were set according to StableBaselines3 standards. The rollout setting was defined such that the agent could search the design space at random, filling the replay buffer with enough experience to prevent the agent from converging to a design space that was not optimal. The replay buffer was sized proportional to the number of training steps due to system memory constraints.  
%
\begin{table}[t]
        \caption{TD3 Training Hyperparameters}
        \vspace{-4mm}
        \label{tab:training_hyperameters}
        \begin{center}
        \begin{tabular}{|c||c|}
        \hline
        Hyperparameter                     & Value                           \\
        \hline
        Learning Rate, $\alpha$         & 0.001                           \\
        Learning Starts                 & 100 Steps                       \\
        Batch Size                      & 100 Transitions                 \\
        Tau, $\tau$                     & 0.005                           \\
        Gamma, $\gamma$                 & 0.99                            \\
        Training Frequency              & 1:Episode                       \\
        Gradient Steps                  & $\propto$ Training Frequency    \\
        Action Noise,  $\epsilon$       & None                            \\
        Policy Delay                    & 1 : 2 Q-Function Updates        \\
        Target Policy Noise, $\epsilon$ & 0.2                             \\
        Target Policy Clip, $c$         & 0.5                             \\
        Seed                            & 100 Random Seeds                \\
        \hline
        \end{tabular}
        \end{center}
        \vspace{-5mm}
\end{table}
%
%
\begin{table}[t]
        \caption{PPO Training Hyperparameters}
        \vspace{-4mm}
        \label{tab:training_hyperameters_PPO}
        \begin{center}
        \begin{tabular}{|c||c|}
        \hline
        Hyperparameter                  & Value                           \\
        \hline
        Learning Rate, $\alpha$         & 0.001                           \\
        Batch Size                      & 64                              \\
        Clip Range, $\epsilon $         & 0.2                             \\
        Gamma, $\gamma$                 & 0.99                            \\
        GAE-Lambda,                     & 0.95                            \\
        Training Frequency              & 1:Episode                       \\
        Gradient Steps                  & $\propto$ Training Frequency    \\
        Policy Delay                    & 1 : 2 Q-Function Updates        \\
        Target Policy Noise, $\epsilon$ & 0.2                             \\
        Target Policy Clip, $c$         & 0.5                             \\
        Seed                            & 100 Random Seeds                \\
        \hline
        \end{tabular}
        \end{center}
        \vspace{-5mm}
\end{table}
%

The training hyperparameters for PPO found in Table~\ref{tab:training_hyperameters_PPO} were set similarly to TD3's. All the PPO hyperameters, other than learning rate and N-steps, were set according to the algorithm's author and StableBaselines3's recommendations.
The learning rate and N-steps were adjusted as the algorithm was not able to converge within 1000 episodes given the initial hyperparameter values of 0.0003 and 2048.
